Data- and Ontology Paper: Quality Ontology for Handicap Parking Spots around Venues in Amsterdam

### 2016-04-23 milestone2/paper/paper.tex
review section 7 & abstract

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{listings}
\lstset{language=SQL,morekeywords={and, some, exactly}}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words. It should be written using the
\emph{abstract} environment.
\end{abstract}

@@

\subsection{Entities}
The main difference with the previous version of the ontology is that each of the three main classes are now subdivided into more specific subclasses. For example:

\begin{itemize}
	\item \textbf{Events}: Divided into Plays and Exhibitions
	\item \textbf{Venues}: Divided into Theatres and Museums
	\item \textbf{Parking Slots}: Divided into Small, Medium and Large Slots
\end{itemize}

@@

\begin{lstlisting}[captionpos=b, caption=Definition of Large Slot a subclass of Parking Slot, label=lst:owl, basicstyle=\ttfamily\small,frame=bt]
(dbo:location exactly 1 Location)
and (info exactly 1 xsd:string)
and (quantity exactly 1 xsd:unsignedInt)
\end{lstlisting}

- Our Location class extends dbo:Location class in the use of Borough

@@

- Restrictions on datatype properties. Cardinalities are explicit, so that they reflect that an Event has only one Venue, for example

- Introduce 'Event venue' which has subproperties 'Exhibition Venue' and 'Play Venue' depending on their range. Also introduce its inverse 'Venue Events'

- We create a subproperty of dbo:location to be 'venue location'. We restrict dbo:location to have domain Parking Slots while 'venue location' has domain Venues. Both have Location as range.

- Properties for Borough, City and Country

\section{Section 6 - The Dataset}
\textit{Describe how you recasted the dataset(s) of the previous assignment to the new ontology (perhaps you found other datasets that you want to add). What did it take to do this? What metadata have you published alongside the dataset, and how did you generate it? (Provenance, VOID, etc.) Describe how your data meeds the 5 star model for Linked Data.}

\section{Section 7 - Evaluation}
\textit{Evaluate the ontology and dataset with respect to each other (does the ontology really sanction only the intended inference) and with respect to the requirements and use case (extend your application?!). You may want to analyze the ontology using some quality criteria from the literature.}

\subsection{Comparison with the dataset}
%TODO insert queries

\subsection{Comparison with requirements}
\begin{enumerate}
	\item Search by interests: Initial division of events and Venues by personal interest.
	\item Detailed location information: Ability to search for Venues and Parking Slots in same Borough is simple.
	\item Detailed information about Parking Slots: Size is explicit
\end{enumerate}

\subsection{Evaluate according to five stars}
- Usage of other ontologies like dbo and geo
- Metadata ?

>>>>

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{listings}
\lstset{language=SQL,morekeywords={and, some, exactly}}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}

@@

\begin{abstract}
% The abstract should summarize the contents of the paper and should
% contain at least 70 and at most 150 words. It should be written using the
% \emph{abstract} environment.
We introduce a Linked Dataset integrating three different datasets related to
the city of Amsterdam. We present the details of the dataset and the ontology
that we introduce to cover all the important concepts of those data. Also we
provide a thoughtful analysis of the methodology that we applied and the
evaluation techniques that have been embraced. We enhanced our previous dataset
with a richer ontology and we show how we published our results following the
5-star model for Linked Data.
\end{abstract}

@@

\subsection{Entities}
The main difference with the previous version of the ontology is that each of the three main classes are now subdivided into more specific subclasses. For example:
\begin{itemize}
	\item \textbf{Events}: Divided into Plays and Exhibitions
	\item \textbf{Venues}: Divided into Theatres and Museums
	\item \textbf{Parking Slots}: Divided into Small, Medium and Large Slots
\end{itemize}
A visualization of the current class hierarchy is given in Figure
\ref{fig:ontology-classes}.

\begin{figure}[h] \centering
	\includegraphics[width=.9\textwidth]{img/ontology-classes.png}
	\caption{Class hierarchy for the current version of the Find A Slot ontology.}
	\label{fig:ontology-classes}
\end{figure}

@@

\begin{lstlisting}[captionpos=b, caption=Definition of Large Slot a subclass of Parking Slot, label=lst:owl, basicstyle=\ttfamily\small,frame=bt,showstringspaces=false]
'Parking Slot' 
and (quantity some xsd:unsignedInt[>= "5"^^xsd:unsignedInt])
\end{lstlisting}

\begin{lstlisting}[captionpos=b, caption=Definition of Medium Slot a subclass of Parking Slot, label=lst:owl, basicstyle=\ttfamily\small,frame=bt,showstringspaces=false]
'Parking Slot' 
and (quantity some xsd:unsignedInt[>= "3"^^xsd:unsignedInt,
 < "5"^^xsd:unsignedInt])
\end{lstlisting}

\begin{lstlisting}[captionpos=b, caption=Definition of Small Slot a subclass of Parking Slot, label=lst:owl, basicstyle=\ttfamily\small,frame=bt,showstringspaces=false]
'Parking Slot' 
 and (quantity some xsd:unsignedInt[>="1"^^xsd:unsignedInt ,
  < "3"^^xsd:unsignedInt])
\end{lstlisting}

The last extension of the entities regards the creation of a class for \textit{Borough} with the purpose to link it to our Location entity. As explained before, we use the dbepedia for the management of location. However, dbo:Location does not include Boroughs, a crucial part of the description of a  location in Amsterdam. Thus, we create a subclass called Location, which is equivalent to a dbo:Location with a Borough, to represent the specific case of locations in Amsterdam.

@@

The first extension in the Properties regards restrictions on datatype properties. We have included cardinalities with respect to the real world. An example can be seen at the Event entity where we state that in order for an Event to be an Event, it also needs to have at least one Venue where it will take place.

Furthermore, we introduced the 'Event venue' property which has sub-properties 'Exhibition Venue' and 'Play Venue' according to their range. If event is an Exhibition then it uses the 'Exhibition Venue' property. We have also introduced the 'Venue Events' property as the inverse property of 'Event venue'.

Moreover we included in our dbo:location property two sub-properties named 'slot location' and 'venue location'. We use these properties to restrict our dbo:location to have domain Parking Slot when we use the 'slot location' property and Venue when we use the 'venue location'. Both of them have Location as range.

The last extension of our properties section refers to the addition of the properties \textit{Borough} , \textit{City} and \textit{Country}. The reason behind this is that we want to have restrictions. In order to ensure that a dbo:location has exactly one country we use the equivalent rule : 
\\

\begin{lstlisting}[captionpos=b, title=Class equivalent to dbo:Location with the use of our subproperties, label=lst:owl, basicstyle=\ttfamily\small,frame=bt]
(city exactly 1 dbo:City) 
and (country exactly 1 dbo:Country) 
and (address exactly 1 xsd:string)
\end{lstlisting}

Similarly for our \textit{Location} the equivalent rule is:

\begin{lstlisting}[captionpos=b, title=Class equivalent to Location with the use of our subproperty orough, label=lst:owl, basicstyle=\ttfamily\small,frame=bt]
dbo:Location 
and (dbo:borough exactly 1 Borough)
\end{lstlisting}

\section{The Dataset}
% Describe how you recasted the dataset(s) of the previous assignment to the new
% ontology (perhaps you found other datasets that you want to add). What did it
% take to do this? What metadata have you published alongside the dataset, and how
% did you generate it? (Provenance, VOID, etc.) Describe how your data meeds the 5
% star model for Linked Data.
The three datasets have been converted to a linked data format using the second
version of the ontology in a straightforward way. We create
resources for the newly introduced \texttt{Borough} class. Cities have been
recasted to point to DBpedia resources (as for countries).
Entities of class \texttt{Museum} or \texttt{Theater} are created based on their
original dataset of provenience. An \texttt{Event} is linked to a
\texttt{Venue} via a newly created object property and this allows the reasoning
engine to infer if an \texttt{Event} is a \texttt{Play} or an \texttt{Exhibition}.

Given the quantity of slots available for a \texttt{ParkingSlot}, thanks to the
new ontology, the dataset distinguishes parking slots based their availability
into \texttt{SmallSlot}, \texttt{MediumSlot} and \texttt{LargeSlot}. This
provides a richer classification of parking slots than based on the quantity
property directly. This is something that we get through inference, so it has
not been directly coded into the conversion script.

Each of the three datasets has been published with its companion VoID dataset,
describing the contents of the dataset it refers to. Most of the metrics and
metadata have been generated using \textbf{rdflib}'s \texttt{generateVoID}
method applied on the three graphs.
Moreover we publish a VoID Linkedset that links together the three datasets as a
new one. Alongside this we provide some additional metadata from the
\texttt{void:}\footnote{\url{http://rdfs.org/ns/void#}} ontology, such as
\texttt{target}, \texttt{sparqlEndpoint} and
\texttt{exampleResource} and from the
\texttt{dcterms:}\footnote{\url{http://purl.org/dc/terms/}} ontology, such as
\texttt{subject}, \texttt{title} and
\texttt{description}. Those additional metadata have been added manually
to the VoID dataset. The \texttt{void:Linkset} can be retrieved at the following
URL \url{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/void}.

\subsection{5-star Open Data}
We say that the published database is conform with standards proposed by the
5-star model for Linked Data \cite{janowicz2014five}. Here we defend our statement by taking each of the
five steps into consideration.

\begin{description}
\item[Available on the Web] We published our data under an open license,
namely the CC0 1.0 Universal (this is declared in the VoID metadata).
\item[Available as structured data] The dataset is available in RDF
format which is structured.
\item[Available as non-proprietary format] Again, our dataset is specified
in a W3C language so it is not in a proprietary format but in an
open and standardized format.
\item[Use URIs to denote things] We use URIs to denote everything that is
not an RDF Literal. Events, Venues, Locations and starting from this version of
the ontology we include countries, cities and boroughs as resources defined by
URIs.
\item[Link to other data] We provide external pointers to resources from
DBpedia such as for cities (e.g. \texttt{dbr:Amsterdam}), countries (e.g.
\texttt{dbr:Netherlands}) or as \texttt{dcterms:subject}, in the VoID
specification, we point to \texttt{dbr:Museums} and \texttt{dbr:Parking\_space}.
\end{description}

\section{Evaluation}
For evaluating our ontology we got inspired by the work of Hlomani and Stacey
\cite{hlomani2014approaches} on ontology evaluation and decided to evaluate our
ontology using three major criteria:
\begin{enumerate}
	\item \textbf{Task-based Evaluation}. First of all we perform a task-based evaluation that typically evaluates how effective our ontology is in the context of an application.
	\item \textbf{User-based Evaluation}. We perform a user-based evaluation that evaluates the ontology through user's experiences. Contrary to task-based evaluation, we are not accessing semantic validity and consistency of our ontology but we focus on the subjective information of it.
	\item \textbf{Data-driven evaluation}. In the last part of this section we focus on evaluating our ontology by comparing it, with existing data about the domain it models.
\end{enumerate}

\subsection{Task-based Evaluation}
\begin{enumerate}
	\item \textbf{Search by interest}.
	With the extension of our ontology we succeed in extending our application. We have enabled the search by interests, as we initially divide Events and Venues with regard to personal interest. This way the users can narrow down their search avoiding nonessential information.

	\item \textbf{Search by Borough}. Another main aspect that adds to the improvement of our ontology are the detailed location information that the users have. Now the users have the ability to search for Venues and Parking Slots in same Borough in a simple way.

	\item \textbf{Capacity of Parking Slots}. We also provide with explicit information about each Parking Slot that is close to the interests of the user. Users now have prior knowledge regarding the capacity of the parking spot they need.
\end{enumerate}

\subsection{User-based Evaluation}
For our user-based evaluation we simply examined our dataset as a \textit{third
user}. The source and the meta data that have been added with the void ontology
provide with important information, not only on each of the three datasets
separately but on the dataset as a whole. \textit{Labels}, \textit{descriptions}
and important \textit{metrics}, such as the total number of triples that exist
in each dataset are only some of the meta-data information that have been added.
However the risk with the specific way of evaluation, is that it is difficult to
establish objective standards as it depends on the different type of users
involved.

\subsection{Data-driven evaluation}
So far our ontology combines knowledge from three different datasets in order to
provide a useful service to the potential users of our application. Compared to
other ontologies in the specific domain of finding parking slots it is clear
that our ontology is quite innovative, since we focus specifically on people
with handicap.

With the addition of Borough as a key feature of Location, the data can be
combined in a more efficient way, increasing the total efficiency of our web
application even further.Besides efficiency, we wanted to check how well our
ontology \textit{fits the domain knowledge} \cite{brewster2004data}.

This was done by comparing ontology concepts derived from the three separate
datasets that we used in milestone 1, with the latest version of our dataset.
So far our ontology fits the domain knowledge of the three datasets, perfectly,
however we realistically acknowledge the fact that there is certainly room for
further improvement in the general domain of Events and Parking Slots.
